---
title: "sim_datasets"
format: html
editor: visual
---

## Creating simulated datasets

We will simulate datasets for a planned clinical trial for fatigue in IBD in the absence of a flare, iron deficiency anemia, or hypothyroidism.

```{r setup}
#| include: false
library(tidyverse)
library(CrossCarry)
```

The trial design includes a crossover design between two treatments, thiamine at 15 mg/kg daily, and modafinil 100 mg bid, with 4 week treatment periods and 4 week washout periods. This will be followed by a 2nd 4 week washout period, then an 8 week trial of wellbutrin.

Fatigue and QoL will be measured at the beginning and end of each period with the appropriate PRO (UCPRO and CDPRO), and with the fatigue instrument, the Inflammatory Bowel Disease-Fatigue Questionnaire. Range is 0-20 from 5 questions to get score 1, with higher scores indicating more fatigue. The median for CD is 9 in remission, 11 in flare. The median for UC is 8 in remission, 11 in flare. Data from *Journal of Crohn's and Colitis*, Volume 8, Issue 11, 1 November 2014, Pages 1398–1406, <https://doi.org/10.1016/j.crohns.2014.04.013>. Improvement is considered a reduction by 3 points.

Questions for Score 1 include

1.1. What is your fatigue level right now

1.2. What was your highest fatigue level in the past 2 weeks

1.3. What was your lowest fatigue level in the past 2 weeks

1.4. What was your average fatigue level in the past 2 weeks

1.5. How much of your waking time have you felt fatigued in the past two weeks

Responses on a 0 (none) to 4 (severe or all of the time) scale - \[these are guesses - need to see legit version of IBD-F\]

0 None, 1 Slight, 2 Somewhat, 3 Moderate, 4 Severe

0 Never, 1 Rarely, 2 Sometimes, 3 Very Often, 4 All of the Time

We will consider 1st order and 2nd order carryover.

There will be 7 study periods. The first six will all be of 4 weeks duration. The last will be of 8 weeks duration (wellbutrin Rx).

| Sequence | Period 1 | Period 2 | Period 3 | Period 4 | Period 5 | Period 6 | Period 7   |
|---------|---------|---------|---------|---------|---------|---------|---------|
| 1 - AAB  | Thi      | Washout  | Thi      | Washout  | Mod      | Washout  | Wellbutrin |
| 2 - ABA  | Thi      | Washout  | Mod      | Washout  | Thi      | Washout  | Wellbutrin |
| 3 - BAA  | Mod      | Washout  | Thi      | Washout  | Thi      | Washout  | Wellbutrin |

: Study Timeline

Now to begin simulating a dataset of fatigue measurements (8 total).

All measurements will occur at the beginning and end of each period

We will start with 10 patients in each group, and a dataset with no carryover at all.

```{r}

baseline = 9
sdev = 2 #get mean and SD data for fatigue from Bager paper
c1 = 0 # half of previous effect size
c2 = 0 # one quarter of 2nd previous effect size 

# effect_T = -3
# effect_M = -4
# effect_W = -5

data1 <- tibble(
  # set up patient_id
  # set up f scores as single col, 
  # set up time point as measurement time 1-8
  # total 240 measurements of fatigue (f)
  subject_id = rep(1:30, each = 8),
  seq = rep(rep(c(1:3), each = 8), 10),
  timepoint = c(rep(1:8, times = 30)),
  # add random noise
  rand1 = rnorm(n = 240, mean = 0, sd = sdev),
  rand2 = rnorm(n = 240, mean = 0, sd = sdev),
  rand3 = rnorm(n = 240, mean = 0, sd = sdev),
  rand4 = rnorm(n = 240, mean = 0, sd = sdev),
  rand5 = rnorm(n = 240, mean = 0, sd = sdev),
  rand6 = rnorm(n = 240, mean = 0, sd = sdev),
  rand7 = rnorm(n = 240, mean = 0, sd = sdev),
  rand8 = rnorm(n = 240, mean = 0, sd = sdev),
  c1 = 0,
  c2 = 0,
  baseline = 9,
  effect = case_when(timepoint == 1 ~ 0,
                     seq == 1 & timepoint == 2 ~ -3,
                     seq == 2 & timepoint == 2 ~ -3,
                     seq == 3 & timepoint == 2 ~ -4,
                     timepoint == 3 ~ 0,
                     seq == 1 & timepoint == 4 ~ -3,
                     seq == 2 & timepoint == 4 ~ -4,
                     seq == 3 & timepoint == 4 ~ -3,
                     timepoint == 5 ~ 0,
                     seq == 1 & timepoint == 6 ~ -4,
                     seq == 2 & timepoint == 6 ~ -3,
                     seq == 3 & timepoint == 6 ~ -3,
                     timepoint == 7 ~ 0, 
                     timepoint == 8 ~ -5),
  fatigue = round(baseline + effect + c1 + c2 +
    case_when(timepoint == 1 ~ rand1,
              timepoint == 2 ~ rand2,
              timepoint == 3 ~ rand3,
              timepoint == 4 ~ rand4,
              timepoint == 5 ~ rand5,
              timepoint == 6 ~ rand6,
              timepoint == 7 ~ rand7,
              timepoint == 8 ~ rand8
              ))
)

data2 <- data1 |> 
  select(subject_id, timepoint, seq, fatigue) |> 
  pivot_wider(id_cols = c(subject_id, seq), names_from = timepoint, names_prefix = "tmpt_", values_from = fatigue)
 
data2_long <- data2 |> 
  pivot_longer(cols = tmpt_1:tmpt_8,names_prefix = "tmpt_", names_to = "timepoint", values_to = "fatigue")
  # define c1 depending on seq and period
  # define c2 depending on seq and period

```

This creates 3 data sets with a 1st order carryover of 0, and a 2nd order carryover of 0.

data1 is tall, with all of the input vars, including random noise at each time point.

data2 is wide, with only subject_id, sequence, and fatigue score at each time point.

data2_long is the same as data2 but in long format.

Need to add treatment, period to use package.

Look at CrossCarry::Arterial data for example

```{r}
CrossCarry::Arterial 
```
